Diverse Genotype-by-Weather Interactions in Switchgrass

### 2024-07-17 manuscript/revision2/response_to_reviews/response_to_reviews.tex

- There appears to be an issue with the construction of the
hypothesis-derived covariance matrices. I believe the goal here is to
estimate the genetic covariance among gardens based on the phenotypic
covariance (P) and the estimated residual covariance (E), where P = G +
E. The described approach involves starting with the the phenotypic
correlation matrix and then replacing the diagonal with the coefficient
of variation. If the diagonal had been replaced with the h2 in each
garden, that'd be a valid estimate of G. But as described, it's likely
that you'll end up with an invalid covariance matrix, one that's not
positive-semi-definite. Instead the appropriate operation would be to
both pre- and post-multiply the covariance matrix by a diagonal matrix
with the square-root of the CV's. This maintains a valid covariance-like
structure. Or just mean-standardize the traits first and then calculate
the covariance of this standardized matrix.

\end{tcolorbox}
\end{quote}

@@

We now use the narrow-sense heritability as the diagonal for each
GxWeather matrix, and clarify this in the Supplementary Methods (SI
Appendix, Section S1, first and eighth paragraph - first and last
paragraph on page two).

\begin{quote}
\begin{tcolorbox}[enhanced jigsaw, colframe=quarto-callout-warning-color-frame, rightrule=.15mm, leftrule=.75mm, left=2mm, breakable, toprule=.15mm, arc=.35mm, bottomrule=.15mm, opacityback=0, colback=white]

- Antagonistic Pleiotropy: Maybe I'm missing the idea of this analysis,
but it doesn't seem to me that this strategy for partitioning loci
between antagonistic pleiotropy and differential sensitivity would have
equal power to detect each class. It seems that antagonistic pleiotropy
should be a subset of differential sensitivity because the latter is
defined as simply a change in magnitude. But even if it's restricted to
``different magnitude but same sign'', the practical definition here
seems to be that antagonistic pleiotropy is detected when the signs are
different and both lfsrs \textless{} threshold (0.05?), while
differential sensitivity additionally requires a threshold on the
difference in effect sizes (0.4) with no justification for why this size
was chosen. This additional criterion will necessarily make the rate of
detection different. Even without this, with differential sensitivity
one effect size must be much larger than the other in absolute value
(which isn't the case with antagonistic pleiotropy), so differential
sensitivity loci will be more likely to pass the lfsr loci than
antagonistic pleiotropy loci. Note that previous literature here tried
to separate antagonistic pleiotropy from conditional neutrality (ie
where in one location the effect was zero), while here the contrast is
with differential sensitivity where effects are non-zero in all
locations. I'm not aware of previous discussions in the literature of
trying to differentiate these two specific classes of GxE variants and
not really sure theoretically what the importance would be.

\end{tcolorbox}
\end{quote}

We believe that the use of the lfsr to detect effects with rank-changing
GxE is a key advance in our manuscript, and so we have made changes to
the Introduction (lines 169-171), Results (lines 319-326), and Materials
\& Methods (lines 957-997; lines 1055-1056) to explain and motivate this
statistical change.

Our expectation is that in nature, effects will always differ.
Statistically, this difference will not always be detectable. Thus,
rather than ask ``Are these two effects different?'' - as we reasonably
expect two effects to be, even if this difference cannot be measured -
the local false sign rate answers a more meaningful question: Can we be
confident in the sign of this effect?

@@

We think that if evolutionary geneticists are interested in antagonistic
pleiotropy and rank-changing GxE, then they should use the lfsr to
measure their confidence in the sign of the effect, rather than using
statistical tests where the null hypothesis is that the effect is
different than zero. However, if we use the lfsr, comparisons between
antagonistic pleiotropy and conditional neutrality are no longer
sensible, as we are no longer doing a statistical test that can robustly
detect conditional neutrality (just as the FDR does not robustly detect
antagonistic pleiotropy). This is justified because detection of
antagonistic pleiotropy is more important than detection of conditional
neutrality for models of local adaptation.

It's true that the threshold for differential sensitivity is arbitrary.
We have reworded the manuscript to stress that there is equal power to
detect effects of different sign as there are effects of the same sign
(lines 994-997; lines 1055-1056). Another class of effects we have in
our analysis that differ from classic antagonistic pleiotropy \&
conditional neutrality comparisons are effects which are not
distinguishable by sign or magnitude. It is not accurate that
differentially sensitive loci will be more likely to pass the lfsr,
because the loci are first selected by significant lfsr, then divided
further into effects that can \& cannot be distinguished by magnitude.
Thus effects that are significant, but have small magnitude in both
conditions will be labeled as not being distinguishable - essentially,
these effects do not have detectable GxE. Effects without GxE may be
even more common and should also be quantified. We propose that, if our
intent is to detect sign-changing GxE, then we should use an unbiased
statistical test to look at loci with and without sign-changing GxE, the
lfsr.

~

~

\begin{center}
Best,

\end{center}

\begin{flushright}
Alice MacQueen and Tom Juenger

\end{flushright}

\end{document}
